Prediction is Hard (Especially About the Future)

### 2015-08-09 Manuscript.tex
Updates from ShareLaTeX

>>>>

Trustworthy domain models are a popular alternatives to CBR planners. In our previous work, we have used executing source code as a "model" to check if our mutations to test suites minimize the test suite size while maximizing the number of statements covered~\cite{me09m,andrews07,andrews10}. However, we do not always have access to ready-to-use models. Further, finding empirical data to validate existing models can be hard. Fortunately, this issue can be circumvented by
